---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# twitchr

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![R-CMD-check](https://github.com/KoderKow/twitchr/workflows/R-CMD-check/badge.svg)](https://github.com/KoderKow/twitchr/actions)
<!-- badges: end -->

R wrapper for the Twitch API.

## Installation

### From Github

```{r, eval=FALSE}
if (!requireNamespace("remotes")){install.packages("remotes")}
remotes::install_github("koderkow/twitchr")
```

## Setup

### Steps

1. Go to https://dev.twitch.tv/login
2. Login with Twitch
3. Click *Register Your Application*
4. Fill out the App information
    - Name: Name of the app. Something to label it for the own personal use
    - OAuth Redirect URLs: Fill this in if one if you have one. If not put `http://localhost`
    - Category: Pick related category such as *Analytics Tool*
5. Click Create
6. On the new app, click *Manage*
7. This page will have the Client ID and Client Secret
8. Open the `.Renviron` to add these values
    - Run `usethis::edit_r_environ()` in the RStudio R console
9. Enter the two key values into this file with the following key names
    - `TWITCH_CLIENT_ID=YOUR CLIENT ID`
    - `TWITCH_SECRET=YOUR SECRET`
10. Restart the RStudio session

### More Information

Read about getting authorization tokens [here](https://dev.twitch.tv/docs/authentication/).

## Examples

```{r}
library(twitchr)
```

### Authorize

Get auth token by using `twitch_auth()`. This will be appended to future API calls

```{r}
twitch_auth()
```

### Get user information

Look up a user by their display name to get user information. This is userful to obtain `broadcaster_id` for other functions

```{r}
user <- get_users(login = "theeatgamelove")

user
```

### Get Videos

Obtain a users recent videos 

```{r}
videos <- get_videos(user_id = user$id)
```

### Get Followers

Display the followers of a channel

```{r}
followers <- get_follows(to_id = user$id)
```

### Get chatters

Display who is currently in a broadcasters chat

```{r}
chatters <- get_chatters("theeatgamelove")
```

### Other functions

I have covered most of the Twitch API endpoints which can be viewed [here](https://koderkow.github.io/twitchr/reference/index.html). If there are any you would like added please create an issue! :)

## Thanks to

- [Freguglia](https://github.com/Freguglia/rTwitchAPI/) for getting me started on the oauth code
